---
title: "Psuedo A/B Testing (EDA Part) by Qing Li"
output:
  html_document:
    df_print: paged
---
#Background Information of the Data Set

This is a psuedo data set of an A/B Testing process for a E-Business company.The data shows user's activities on an online sales website. An experiment was launched on day 4 with a goal to increase users' click through rate(clicks/views) and total revenue.

Note: first 3 days no experiment, 4th-14th days experiment running

#Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE}
#get the data and explore the structure
setwd("/Users/wall-e/Downloads")
ab_data<-read.csv('abtest_example_ctr copy.csv')
str(ab_data)
summary(ab_data)
```

Data subsetting and cleaning:

```{r echo=FALSE, message=FALSE, warning=FALSE}
#new data set for EDA
library(dplyr)
ab2<-ab_data %>%
  select(X0, country, groups, deviceid, device, sellerid, itemid, date, views, 
         clicks, revenue) %>%
  filter(!date %in% c('5/8/17', '5/9/17', '5/10/17')) %>%
  mutate(X0=as.factor(X0), deviceid=as.factor(deviceid), 
         sellerid=as.factor(sellerid), itemid=as.factor(itemid)) %>%
  mutate(ctr=ifelse(clicks==0, 0, views/clicks))
str(ab2)
```

After cleaning, the new data set has 18107 records of 12 variables. 

Conlusion for the new dataset: 

```{r echo=FALSE, message=FALSE, warning=FALSE}
ab2%>%
  group_by(groups) %>%
  summarise(mean_click=mean(clicks),
            median_click=median(clicks),
            mean_view=mean(views),
            median_view=median(views),
            mean_ctr=mean(ctr),
            median_ctr=median(ctr),
            mean_revenue=mean(revenue),
            median_revenue=median(revenue),
            n=n())
```

From the above data, we can guess that the treatment does not really contribute to a higher ctr and revenue. 

Histograms:

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
ggplot(ab2, aes(revenue))+geom_histogram()+xlab("Revenue (in $)")
ggplot(ab2, aes(revenue))+geom_histogram(binwidth=10)+xlim(0,300)+
  ylim(0,175)+
  xlab("Revenue (in $)")+
  ggtitle("Revenue Distribution Among Users who Made Purchases(Revenue>$0)")

```

The histograms shows that the most users don't make any purchase (revenue=0), and among the users who did make purchase, there's a gap between more price-sensitive users (purchase between around 50 dollars to 75 dollars) to the less price-sensitive groups (purchase about 125 dollars and above). 


```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(ab2, aes(ctr))+geom_histogram()
ggplot(ab2, aes(ctr))+geom_histogram(binwidth=0.5)+xlim(0,15)+ylim(0,600)


```

In terms of the CTR, again more users did not make the clicks. And among the ones who clicked, there seems to be gaps everywhere, especially between around 2 to 4, and most of the clicking users' CTR are somewhere from 2 to 10 clicks per view.  


```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(ab2, aes(clicks))+geom_histogram()
ggplot(ab2, aes(clicks))+geom_histogram(binwidth=1)+xlim(0,7)

```

The trends shows that less users make more clicks on the page, and the more clicks, the less users will make. 


```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(ab2, aes(views))+geom_histogram()
ggplot(ab2, aes(views))+geom_histogram(binwidth=1)+xlim(0,17)

```

Among all the histograms, this one is closest to normal, although a little right-skewed. This means that the experiment design is fine in terms of the showing frequency of the webpage.

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(ab2, aes(date))+geom_bar()

```

Dates are spreaded evenly.

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(ab2, aes(country))+geom_bar()

```

US has the most users in this experiment. This makes sense since for most US companies, US is usually their largest market, or main market. However, if this is not the case for this company, the data would likely to be not representative enough.

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(ab2, aes(device))+geom_bar()

```

Most users are using Android device, followed by Web users, followed by Ios and Others. This looks a little wierd to me, since from my common sense web users should be the ones who make the most purchase from an e-business website, and most treatments which are connected to CTR are for websites. 

This might be a potential problem of the sample choosing of the experiment, unless evidence shows that Android users are definitely the major users for the company.


#Univariate Analysis

#What is the structure of your dataset?

The raw dataset has 22960 records of 15 variables(X0=customerid, country, groups, deviceid, device, sellerid, itemid, date, views, clicks, revenue, Row.Labels, Sum.of.clicks, Sum.of.revenue, Count.of.0).

To clean the data for further EDA process, I make subset of only the 4th to 14th day, which is 5/11/17-5/21/17, and delete the last few variables. The following variables have stayed: X0(=customerid), country, groups, deviceid, device, sellerid, itemid, date, views, clicks, revenue. And records has been decreased to 18107. 

#What is/are the main feature(s) of interest in your dataset?

The main features in the data set are groups, click through rate(CTR), which is clicks/views, and revenue. I'd like to determine if the treatment really matters in an increase of CTR and revenue, and which other features can also be taken into consideration to build a predictive model to the effect.   

#What other features in the dataset do you think will help support your investigation into your feature(s) of interest?

Country, groups, device, and date are all likely to contribute to the CTR and revenue of the experiment. My expectation is that the group contribute the most to it, since this in an A/B test means that the change can actually cause a positive business result. 

#Did you create any new variables from existing variables in the dataset?

I created a CTR variable by dividing clicks by views. The only exception is that if the click is 0, which I made directly 0 to avoid mathmetical error. 

#Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?

As I mentioned above, Android users might took too much proportion of the data, which might cause the dataset not representative enough for the real market. 

#Bivariate Plots Section

Overview:

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(GGally)

ggpairs(ab2,c(2,3,5,8:12))

```

1. Groups does not really matter in this tests, however it also shows that the views assigned to each groups is approximately the same, which shows their's no noises in this part of the experiment design. This can be furtherly confirmed by the side-by-side boxplots of the views by groups. The side-by-side boxplots of clicks, revenue and CTR also supports that the group is not really correlated to the differences.

2. It seems like devices and countries also express very few information about the revenue and CTR difference. The shapes of the histograms and the boxplots of the two groups are again very similar. 

3. Date, as a factor, does matter more than group, device and country in explaining CTR and revenue differences. Both the faced histograms and the side-by-side boxplots show this.

Plots in details:

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Discrete vs Discrete Variables:

#Views vs. Clicks in heatmap
ggplot(data=ab2, aes(x=as.factor(views),y=as.factor(clicks)))+
  geom_bin2d()+
  geom_smooth()+
  ylab("Views Count")+
  xlab("Clicks Count")

#Discrete vs Continuous Variables:

#Views vs. Revenue in jitter plots
ggplot(data=ab2, aes(x=views,y=revenue))+geom_jitter(color='green',alpha=1/5)+
  geom_smooth()+
  ylab("Revenue (in $)")+
  ylim(0,800)
#since there's too many zero points, I re-examed all the non-zero points

#Non-zero Views vs. Revenue in violin plots with boxplot
ggplot(data=subset(ab2,views>0 & revenue >0), 
       aes(x=as.factor(views),y=revenue))+
  geom_violin(trim=F,color='blue')+geom_boxplot(width=0.3)+
  ylab("Revenue (in $)")+
  xlab("Views Count")
 

```

From the plots, views is positively correlated with clicks, but not obviously positively correlated to the revenue, which is the same as the ggpair/overview part shows. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Clicks vs. Revenue in jitter plots
ggplot(data=ab2, aes(x=clicks,y=revenue))+geom_jitter(color='red',alpha=1/5)+
  geom_smooth()+
  ylab("Revenue (in $)")#Again, since there's too many zero points, I re-examed all the non-zero points

#Non-zero Clicks vs. Revenue in violin plots with boxplot
ggplot(data=subset(ab2,clicks>0 & revenue >0), 
       aes(x=as.factor(clicks),y=revenue))+
  geom_violin(trim=F,color='gold')+geom_boxplot(width=0.3)+
  ylab("Revenue (in $)")

#CTR vs. Revenue
ggplot(data=ab2, aes(x=ctr,y=revenue))+geom_jitter(color='navy',alpha=1/5)+
  geom_smooth()+
  ylab("Revenue (in $)")

```

Regarding clicks and revenue, it is not very obviously positively correlated. And the fact that relation between ctr and revenue is not positively correlated is the same as the ggpair/overview result. 

More plots:

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Device vs. Clicks
ggplot(data=ab2, aes(x=device,y=as.factor(clicks)))+geom_bin2d()+geom_smooth()+
  ylab("Click Count")

#Device vs. Views
ggplot(data=ab2, aes(x=device,y=as.factor(views)))+geom_bin2d()+geom_smooth()+
  ylab("View Count")

#Device vs. non-zero CTR
ggplot(data=subset(ab2, ctr>0), aes(x=device,y=ctr))+
  geom_violin(trim=F,color='green')+geom_boxplot(width=0.3)+
   ggtitle("Violin & Boxplot of CTR for Users Who Made Clicks by Device")
  

#Device vs. non-zero Revenue
ggplot(data=subset(ab2, revenue>0), aes(x=device,y=revenue))+
  geom_violin(trim=F,color='navy')+geom_boxplot(width=0.3)+
  ggtitle("Violin & Boxplot of Revenue for Users Who Made Purchases by Device")+
  ylab("Revenue (in $)")


#Date vs. Non-zero CTR
ggplot(data=subset(ab2, ctr>0), aes(x=date,y=ctr))+
  geom_violin(trim=F,color='red')+geom_boxplot(width=0.3)+
  ggtitle("Violin & Boxplot of CTR for Users Who Made Clicks by Date")


#Date vs. Non-zero Revenue
ggplot(data=subset(ab2, revenue>0), aes(x=date,y=revenue))+
  geom_violin(trim=F,color='gold')+geom_boxplot(width=0.3)+
  ggtitle("Violin & Boxplot of Revenue for Users Who Made Purchases by Date")+
  ylab("Revenue (in $)")

```

Here, the fact that even some of the Android users are giving the highest views, it is still the web users who contributed in a higher clicks kind of confirms my previous concern--the sampling issue that Android users takes more proportion than web users, who are more likely to contribute to the clicks and more valuable in terms of CTR. 

CTR seems to be corresponded to the sample proportion--Android users contribute slightly more than others. 

And in terms of revenue, Android users and Web users don't have an obvious advantage, especially compared to the Ios users, although they have been assigned more in the sample. 

Accordingly, the Android users might have skewed the relation of CTR to reveune a lot--it takes the most proportion of the sample, contribute to the most of CTR with the 
lowest contribution of revenue.

In terms of date, the CTR and revenue spreads approximately evenly.

#Bivariate Analysis

#Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

Views have the most obvious positively correlation with the clicks. Although weaker, clicks are also positively correlated to the reveune. 

#What was the strongest relationship you found?

Clicks and views has a correlation of 0.48, which is comparatively the highest in this dataset. The scatterplot of views and clicks also shows that there is an increasing trend between the two factors. 


#Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

The correlation of CTR and revenue is less than 0.1, which is very low in this experiment. In other words, CTR is not correlated that much to the revenue in this experiment.


#Multivariate Plots Section

The histograms shows that the treatment group is not that different from the control group in terms of the revenue. Even the country, date and device structure of the histograms showed very high similarities bwteen the two groups. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(ab2, aes(ctr,fill=country))+geom_histogram(binwidth=0.5)+
  facet_wrap(~groups)
ggplot(ab2, aes(ctr,fill=country))+geom_histogram(binwidth=0.5)+
  facet_wrap(~groups)+xlim(0,15)+ylim(0,700)

ggplot(ab2, aes(ctr,fill=date))+geom_histogram(binwidth=0.5)+
  facet_wrap(~groups)
ggplot(ab2, aes(ctr,fill=date))+geom_histogram(binwidth=0.5)+
  facet_wrap(~groups)+xlim(0,15)+ylim(0,700)

ggplot(ab2, aes(ctr,fill=device))+geom_histogram(binwidth=0.5)+
  facet_wrap(~groups)
ggplot(ab2, aes(ctr,fill=device))+geom_histogram(binwidth=0.5)+
  facet_wrap(~groups)+xlim(0,15)+ylim(0,700)

```

The situation is the same for CTR--the control group and the treatment group don't have noticeble difference.

Group differences in each variables:

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(gridExtra)

#CTR vs. Revenue by groups
ggplot(aes(x=ctr, y=revenue), data=subset(ab2,!is.na(ctr&revenue)))+
  geom_jitter(aes(color=groups),alpha=1/5)+
  geom_smooth(color='gold')+
  ylab("Revenue (in $)")

#Views vs. Clicks by groups
ggplot(aes(x=as.factor(views), y=as.factor(clicks)), 
       data=subset(ab2,!is.na(ctr&revenue)))+
  geom_bin2d()+
  facet_wrap(~groups)+
  ylab("Click Count")+
  xlab("View Count")

#Views vs. Revenue by groups
ggplot(aes(x=as.factor(views), y=revenue),
       data=subset(ab2,!is.na(ctr&revenue)&ctr>0&revenue>0))+
  geom_violin(aes(color=groups))+
  geom_boxplot(width=0.2)+
  ylab("Revenue (in $)")+
  xlab("View Count")
  
#Clicks vs. Revenue by groups
ggplot(aes(x=as.factor(clicks), y=revenue), 
       data=subset(ab2,!is.na(ctr&revenue)&ctr>0&revenue>0))+
  geom_violin(aes(color=groups))+
  geom_boxplot(width=0.1)+
  ylab("Revenue (in $)")+
  xlab("Click Count")

```

As shown above, in terms of revenue, there is a few outliers which generates significantly higher revenue than others with comparatively low views and clicks. Therefore, the graphs might be overfitted by those outliers, who are likely consumers that comparatively makes more purchase than others.

And group does not seem to make any difference in terms of view, clicks, and revenue. 


```{r echo=FALSE, message=FALSE, warning=FALSE}

quantile(ab2$revenue)[2]-1.5*IQR(ab2$revenue)
quantile(ab2$revenue)[4]+1.5*IQR(ab2$revenue) # Quantiles show that users want make purchases unless they are outliers.  

#CTR vs. Revenue by groups
ggplot(aes(x=ctr, y=revenue), data=subset(ab2,!is.na(ctr&revenue)&revenue>0))+
  geom_jitter(aes(color=groups),alpha=0.5)+
  geom_smooth(color='gold')+
  ylim(0,quantile(ab2$revenue,.95))+
  ylab("Revenue (in $)")

```

The points I removed are not really statistically outliers, since most statistically, whoever spent over $0 are all outliers. Instead, I trimed the top 5% of the data, since very likely they are just individuals that likes to make purchase from this company. 

CTR is still not positively correlated to the revenue among the bottom 95% of the users; rather, it has some slightly negative correlation. 

And groups still does not seem to matter. 


```{r echo=FALSE, message=FALSE, warning=FALSE}
# More solid evidence--correlations

#clicks vs. revenue
with(subset(ab2,revenue<=quantile(ab2$revenue,.95)),
     cor.test(clicks,revenue,method='pearson'))
with(subset(ab2,revenue<=quantile(ab2$revenue,.95)),
     cor.test(clicks,revenue,method='spearman'))

#views vs. revenue
with(subset(ab2,revenue<=quantile(ab2$revenue,.95)),
     cor.test(views,revenue,method='pearson'))
with(subset(ab2,revenue<=quantile(ab2$revenue,.95)),
     cor.test(views,revenue,method='spearman'))

#CTR vs. revenue
with(subset(ab2,revenue<=quantile(ab2$revenue,.95)),
     cor.test(ctr,revenue,method='pearson'))
with(subset(ab2,revenue<=quantile(ab2$revenue,.95)),
     cor.test(ctr,revenue,method='spearman'))

```

Above data confirmed with the guess from the plots--among the bottom 95% of the data, both clicks and views, especially clicks, independently, have higher correlation than CTR with the revenue. 

More plots with other factors:

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(data=ab2,aes(x=ctr,y=revenue))+
  geom_point(aes(color=groups))+
  geom_smooth()+
  facet_wrap(~date)+
  ylab("Revenue (in $)") #group by date

ggplot(data=ab2,aes(x=ctr,y=revenue))+
  geom_point(aes(color=groups))+
  geom_smooth()+
  facet_wrap(~device)+
  ylab("Revenue (in $)") #by device

ggplot(data=ab2,aes(x=ctr,y=revenue))+
  geom_point(aes(color=groups))+
  geom_smooth()+
  facet_wrap(~country)+
  ylab("Revenue (in $)") #by country

```

Again, since too many users did not make purchases, I decide to look a closer look at the ones who made purchases, which are the group of users that is more informative in this data set to the company.


```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(data=subset(ab2,revenue>0),aes(x=ctr,y=revenue))+
  geom_point(aes(color=groups))+
  geom_smooth(aes(color=groups))+
  facet_wrap(~date)+
  ylab("Revenue (in $)") #group by date

ggplot(data=subset(ab2,revenue>0),aes(x=ctr,y=revenue))+
  geom_point(aes(color=groups))+
  geom_smooth(aes(color=groups))+
  facet_wrap(~device)+
  ylab("Revenue (in $)") #by device

ggplot(data=subset(ab2,revenue>0),aes(x=ctr,y=revenue))+
  geom_point(aes(color=groups))+
  geom_smooth(aes(color=groups))+
  facet_wrap(~country)+
  ylab("Revenue (in $)") #by country

```

As the graphs show: in terms of dates, device and country, although each day/device/country is different, there's really not too much conclusive patterns among these factors and between two groups. Also, the higher ctr definitely does NOT correlated to a higher revenue. 

Again, the treatment group does not really explain any difference from the control group no matter what countries user are from, what devices they are using and on which date of the experiment.

However, the smoothing lines did show a slightly more positive relationship in the treatment group than in the control group for Web users and other users than the two major mobile users.


```{r echo=FALSE, message=FALSE, warning=FALSE}

library(lubridate)
#Linegraphs of revenues vs. dates by devices with users who actually made purchases
date2<-NA
ab2$date2<-mdy(ab2$date)

ggplot(data=subset(ab2,revenue>0),aes(as.Date(date2,"%Y-%m-%d"),revenue))+
  geom_line(aes(color=device),stat="summary",fun.y=median)+
  scale_x_date(date_labels = "%Y-%m-%d")+
  ylab("Revenue (in $)")+
  xlab("Date")

#Linegraphs of revenues vs. dates by countries with users who actually made purchases

ggplot(data=subset(ab2,revenue>0),aes(as.Date(date2,"%Y-%m-%d"),revenue))+
  geom_line(aes(color=country),stat="summary",fun.y=median)+
  scale_x_date(date_labels = "%Y-%m-%d")+
  ylab("Revenue (in $)")+
  xlab("Date")

#Linegraphs of revenues vs. dates by groups with users who actually made purchases

ggplot(data=subset(ab2,revenue>0),aes(as.Date(date2,"%Y-%m-%d"),revenue))+
  geom_line(aes(color=groups),stat="summary",fun.y=median)+
  scale_x_date(date_labels = "%Y-%m-%d")+
  ylab("Revenue (in $)")+
  xlab("Date")

#Linegraphs of ctr vs. dates by groups with users who actually made purchases

ggplot(data=subset(ab2,revenue>0),aes(as.Date(date2,"%Y-%m-%d"),ctr))+
  geom_line(aes(color=groups),stat="summary",fun.y=median)+
  scale_x_date(date_labels = "%Y-%m-%d")+
  xlab("Date")

#Linegraphs of clicks vs. dates by groups with users who actually made purchases

ggplot(data=subset(ab2,revenue>0&clicks>0),
       aes(as.Date(date2,"%Y-%m-%d"),clicks))+
  geom_line(aes(color=groups),stat="summary",fun.y=median)+
  scale_x_date(date_labels = "%Y-%m-%d")+
  ylab("Click Count")+
  xlab("Date")

#Linegraphs of views vs. dates by groups with users who actually made purchases

ggplot(data=subset(ab2,revenue>0&views>0),
       aes(as.Date(date2,"%Y-%m-%d"),views))+
  geom_line(aes(color=groups),stat="summary",fun.y=median)+
  scale_x_date(date_labels = "%Y-%m-%d")+ylim(0,10)+
  ylab("View Count")+
  xlab("Date")


```

Devices and countries are not informative in terms of median revenue variations in the dates. 

However, surprisingly, in terms of grourps, the trends of the median revenues seems to be opposite of one another--on 5/14, the treatment group reaches its local min while the control group reaches a local max. On 05/17, the local max and min switched, and on 5/18 the situation switched back. However, in terms of CTR(or cicks and/or views), the two groups are not so different(PS. in terms of clicks, the median of both groups equal to each other).


Linear Models:

```{r echo=FALSE, message=FALSE, warning=FALSE}
summary(lm(I(revenue)~I(groups),data=ab2))
summary(lm(I(ctr)~I(groups),data=ab2))
summary(lm(I(revenue)~I(ctr)+I(groups),data=ab2))
```

The linear regression models also supports the result that groups does not make statistically significant difference to both ctr and revenue(p>0.05), and even if we can accpet a result with higher p-value, all three models show that the treatment might make less, but not more, ctr and/or revenue.  

#Multivariate Analysis

#Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

In any sense, the experiment data shows that there's no difference between the treatment group and the control group. Without further model buiding, I would guess that the change that the company wants to make will be likely not contribute to any revenue increase.

#Were there any interesting or surprising interactions between features?

The fact that CTR is not more correlated to revenue than clicks and/or views independently really surprised me. Combining information from the Univariate part that most of the users in this experiment are Android users, and CTR is usually more, if not only, applicable to web users, I would guess that this will cause some inaccuracy to the result.


#OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

Yes. I created three linear models of group and CTR, group and revenue, and group with both CTR and revenue. In each model, the p-value of the group factor is not significantly small, indicating that the treatment does not make a positive impact to ctr and/or revenue. 


#Final Plots and Summary

#Plot One-Important Histograms

```{r echo=FALSE, message=FALSE, warning=FALSE}
fp1<-ggplot(ab2, aes(revenue))+
  geom_histogram(color='black',fill='gold')+
  ggtitle("Revenue of All Users")+
  xlab("Revenue (in $)")

fp2<-ggplot(ab2, aes(revenue))+
  geom_histogram(color='black',fill='gold',binwidth=10)+
  xlim(0,300)+ylim(0,175)+
  ggtitle("Revenue of Users Who Purchase")+
  xlab("Revenue (in $)")

fp3<-ggplot(ab2, aes(ctr))+geom_histogram(color='gold',fill='white')+
  ggtitle("CTR of All Users")

fp4<-ggplot(ab2, aes(ctr))+
  geom_histogram(binwidth=0.5,color='gold',fill='white')+
  xlim(0,15)+ylim(0,600)+
  ggtitle("CTR of Users Who Clicked")

fp5<-ggplot(ab2, aes(device))+geom_bar(aes(fill=device))+
  ggtitle("Users by Device")
  
grid.arrange(fp1,fp2,fp3,fp4,fp5)
```

#Description One

Most users in the experiment did not make purchases, and for the ones who did make purchases, the distribution appears to be bimodal--it is likely that there is a gap between users' purchases for some reasons. 
 
Most users either did not click or did not view. For the ones who have clicked, the distribution is slightly right-skewed, which made sense--more users clicked less than 8 times per view. 

A potential issue here apears: more users in the experiment are Androrid users than other device users--if this is only more than Ios users, it might make sense, since Android users take larger market than Ios users. However this makes little sense in terms of Web users--without further evidence, this data might be less representative in this sense.  

#Plot Two-Relations among clicks, views, CTR towards revenue:

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Views vs. Clicks
fp6<-ggplot(aes(x=as.factor(views),y=as.factor(clicks)),
            data=subset(ab2,!is.na(ctr&revenue)))+
  geom_bin2d()+
  ggtitle("Views vs Clicks")+
  ylab("Click Count")+
  xlab("View Count")

#Clicks vs. Revenue
fp7<-ggplot(data=subset(ab2,clicks>0&revenue>0),
            aes(x=as.factor(clicks),y=revenue))+
  geom_violin(color='red')+
  geom_boxplot(width=0.5)+
  ggtitle("Clicks vs. Revenue")+
  ylab("Revenue (in $)")+
  xlab("Click Count")

#CTR vs. Revenue by Clicks
fp8<-ggplot(data=ab2, aes(x=ctr,y=revenue))+
  geom_jitter(aes(color=clicks),alpha=1/8)+
  geom_smooth(color='gold')+
  ggtitle("CTR vs. Revenue by Clicks")+
  ylab("Revenue (in $)")

grid.arrange(fp6,fp7,fp8,nrow=2)

```

#Description Two

Views has positive relation with clicks, and clicks and views both has possitive relation with revenue. However, CTR has no possitive relation with revenue.

And those who contribute more CTRs are NOT the ones clicked more. In other words, they might have less views.

#Plot Three

```{r echo=FALSE, message=FALSE, warning=FALSE}

fp9<-ggplot(data=subset(ab2,ctr>0),aes(groups,ctr))+
  geom_violin(aes(color=groups))+
  geom_boxplot(width=0.3)+
   ggtitle("CTR by A/B Groups")

fp10<-ggplot(data=subset(ab2,revenue>0),aes(groups,revenue))+
  geom_violin(aes(color=groups))+
  geom_boxplot(width=0.3)+
   ggtitle("Revenue by A/B Groups")+
  ylab("Revenue (in $)")

fp11<-ggplot(data=subset(ab2,groups=='control'),aes(x=ctr,y=revenue))+
  geom_point(color='pink')+
  geom_smooth(color='red')+
  ggtitle("CTR vs Revenue for Control")+
  ylab("Revenue (in $)")

fp12<-ggplot(data=subset(ab2,groups=='treatment'),aes(x=ctr,y=revenue))+
  geom_point(color='light blue')+
  geom_smooth(color='blue')+
  ggtitle("CTR vs Revenue for Treatment")+
  ylab("Revenue (in $)")

grid.arrange(fp9,fp10,fp11,fp12,nrow=2)

```

#Description Three

Group does not matter in terms of CTR, revenue or the relationship between CTR and revenue. 

In other words, in this A/B test, the treatment is likely to be not effective, assumming the sample is representative.


#Reflection

This A/B Testing data set includes 22960 samples of 15 variables, and after adjustment 18107 samples of 12 variables. 

The sampling process seems to be randomized with date, make sense in country, but not so ideal in terms of the devices. Although the data shows that the treatment is likely not so effective in terms of both CTR and revenue increase, the not so representative sampling problem might affect the solidity of the result. 

Another surprising result, that CTR is actually not so correlated to the reveunue increase can also be potentially explained by the sampling issue. 


